Numerical simulation and entropy dissipative cure of the carbuncle instability for the shallow water circular hydraulic jump

### 2021-03-09 numerics_paper/version2/numerical_chj.tex
Add affiliations.

\author{
    David I. Ketcheson \and
    Manuel Quezada de Luna
}
\begin{document}

@@

To compute the boundary integrals, we approximate $q$ on each cell edge $\f_{ij}\in\partial S_i$ by the average of the two

>>>>

\author{
    David I. Ketcheson
  \thanks{
    Computer, Electrical, and Mathematical Sciences \& Engineering Division,
    King Abdullah University of Science and Technology, 4700 KAUST, Thuwal
    23955, Saudi Arabia. (\{manuel.quezada, david.ketcheson\}@kaust.edu.sa).
  }
    \and
    Manuel Quezada de Luna
  \footnotemark[1]
}
\begin{document}

@@

To compute the boundary integrals, we approximate $q$ on each cell edge $\f_{ij}$ by the average of the two
